Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-07-06 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
edits to paper, after karen's comments

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. %Each linear Lagrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
} \\
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion). Right: local error contributions. }
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \Cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\includegraphics[width=0.8\textwidth]{baseSeries/err_est_v2.pdf}
%\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used. In this case, only two refinement iterations are necessary to achieve the target relative QoI error (dotted line).}
\label{fig:baseErr}
\end{figure}
%

@@

\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. 
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_0$ ($0\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
} \\
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
} \\
\subfloat[MF$_2$ ($20\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
} \\
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\subfloat[MF$_6$ ($60\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
}
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion). Right: local error contributions. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to \Cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models.

\Cref{fig:svfRefParams} shows the inferred parameters using some of the mixed-fidelity models and the high-fidelity model.
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
	\label{subfig:svfparamMF1}
} \\
\subfloat[MF$_3$ ($30\%$ HF)]{
	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
	\label{subfig:svfparamMF3}
} \\
\subfloat[MF$_6$ ($60\%$ HF)]{
  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
  \label{subfig:svfparamMF6}
} \\
\subfloat[HF]{
	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
	\label{subfig:svfparamHF}
}
\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models. All figures share the color-scale for the high-fidelity plot.}
\label{fig:svfRefParams}
\end{figure}
%
The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\includegraphics[width=0.8\textwidth]{svf/err_est_v2.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used. The dotted line indicates the target relative QoI error.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare \Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}). We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI. Note that although the inferred parameters in the first and third mixed-fidelity models (see \Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models. These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.

>>>>

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. %Each linear Lagrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.pdf} %0.49 round1 png
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.pdf} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.pdf} %0.49 round1 png
} \\
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion). Right: local error contributions. }
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \Cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\includegraphics[width=\textwidth]{baseSeries/err_est_v2.pdf}
%\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used. In this case, only two refinement iterations are necessary to achieve the target relative QoI error (dotted line).}
\label{fig:baseErr}
\end{figure}
%

@@

\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. 
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_0$ ($0\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_LF_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_LF.pdf} %0.49 round1 png
} \\
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF01_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF01.pdf} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($20\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF02_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF02.pdf} %0.49 round1 png
} \\
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\subfloat[MF$_6$ ($60\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF06_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF06.pdf} %0.49 round1 png
}
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion). Right: local error contributions. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to \Cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models.

\Cref{fig:svfRefParams} shows the inferred parameters using some of the mixed-fidelity models and the high-fidelity model.
%
\begin{figure}[htbp]
\centering
%\subfloat[MF$_1$ ($10\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF1}
%} \\
%\subfloat[MF$_3$ ($30\%$ HF)]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
%	\label{subfig:svfparamMF3}
%} \\
%\subfloat[MF$_6$ ($60\%$ HF)]{
%  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
%  \label{subfig:svfparamMF6}
%} \\
%\subfloat[HF]{
%	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
%	\label{subfig:svfparamHF}
%}
%\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models. All figures share the color-scale for the high-fidelity plot.}
\includegraphics[width=0.95\textwidth]{svf/svf_param_fused.pdf}
\caption{Inferred parameters using mixed-fidelity (top three) and high-fidelity (bottom) models. All figures share the color-scale for the high-fidelity plot.}
\label{fig:svfRefParams}
\end{figure}
%
The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\includegraphics[width=\textwidth]{svf/err_est_v2.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used. The dotted line indicates the target relative QoI error.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare 
%\Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}
the bottom two figures of \Cref{fig:svfRefParams}
). We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI. Note that although the inferred parameters in the first and third mixed-fidelity models (see 
%\Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}
the top two figures of \Cref{fig:svfRefParams}
) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models. These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.
